Electromagnetism Assignment One

### 2016-10-08 em/latex/HW1.tex
Make qm/Makefile work much better, clean up .gitignore as well.

\title{Quantum Mechanics Assignment One}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

We first apply the Laplace Equation:

@@

\begin{align*}
  \int\int\int\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_1) \phi_2 dxdydz &=
  \int\int\int\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_2) \phi_1 dxdydz
\end{align*}

@@

\begin{align*}
  \int\int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_1\phi_2\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  \int\int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_2\phi_1\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

@@

\begin{align*}
  -\int\int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  -\int\int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

@@

\begin{align*}
  \int V_{AB}(\vec{R})\rho_A(\vec{r})dV &= \int V_{BA}(\vec{r})\rho_B(\vec{r})dV\\
\end{align*}

Because A and B are conductors, we know that their potentials $V_{AB}$ and $V{BA}$ are constant. Thus we can remove them from the integral:

@@

NOTE: $V_{A} = V_{AA} + V_{AB}$ is constant, but is $V_{AB}$ constant?\\

@@

The first term $-E_0r\cos\theta$ is the potential from the external field. The second term $\frac{E_0a^3\cos\theta}{r^2}$ is the term due
to the sphere. This term can be rewritten as the dipole term in the multipole expansion:\\

\begin{align*}
  \frac{E_0a\cos\theta}{r^2} &= \frac{1}{4\pi\epsilon_0}\frac{1}{r^2} \hat{r} \cdot \vec{p}\\
\end{align*}

>>>>

\title{Electromagnetism Assignment One}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

We first briefly solve the problem in one dimension to show how it is done:

\begin{align*}
  \int\rho_1\phi_2d^3\vec{r} &= \int\rho_2\phi_1d^3\vec{r}\\
  -\epsilon\int \frac{\partial^2\phi_1}{\partial x^2}\phi_2dx &= -\epsilon\int \frac{\partial^2\phi_2}{\partial x^2}\phi_1dx\\
  \int \frac{\partial^2\phi_1}{\partial x^2}\phi_2dx &= \int \frac{\partial^2\phi_2}{\partial x^2}\phi_1dx\\
  \frac{\partial \phi_1}{\partial x} \phi_2 \Big|_{-\infty}^{\infty} -
  \int \frac{\partial \phi_2}{\partial x}\frac{\partial \phi_1}{\partial x}dx&=
  \frac{\partial \phi_2}{\partial x} \phi_1 \Big|_{-\infty}^{\infty} -
  \int \frac{\partial \phi_1}{\partial x}\frac{\partial \phi_2}{\partial x}dx\\
  \int \frac{\partial \phi_2}{\partial x}\frac{\partial \phi_1}{\partial x}dx&=
  \int \frac{\partial \phi_2}{\partial x}\frac{\partial \phi_1}{\partial x}dx
\end{align*}

Now in 3D. We first apply the Laplace Equation:

@@

\begin{align*}
  \int\int\int\left(\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_1) \phi_2\right) dxdydz &=
  \int\int\int\left(\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_2) \phi_1\right) dxdydz
\end{align*}

@@

\begin{align*}
  \int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_1\phi_2\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  \int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_2\phi_1\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

@@

\begin{align*}
  \int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  \int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

@@

\begin{align*}
  \int V_{AB}(\vec{r})\rho_A(\vec{r})dV &= \int V_{BA}(\vec{r})\rho_B(\vec{r})dV\\
\end{align*}

Because A and B are conductors, we know that their potentials $V_{AB}$ and $V_{BA}$ are constant. Thus we can remove them from the integral:

@@

@@

The first term $-E_0r\cos\theta$ is the potential from the external field. The second term $\frac{E_0a^3\cos\theta}{r^2}$ is the term due
to the sphere. This term can be rewritten as the dipole term in the multipole expansion:
\begin{align*}
  \frac{E_0a\cos\theta}{r^2} &= \frac{1}{4\pi\epsilon_0}\frac{1}{r^2} \hat{r} \cdot \vec{p}
\end{align*}
